A note on multi agent learning

### 2016-06-29 multiAgentLearning/paper/article.tex
added a bunch of text

\abstract{
  %TODO abstract
  \todo[inline]{abstract missing}
}
\todo{be more critical? maybe it depends to much on its paremeters?
  Or which game types are good for saticifing play?
}
\todo{misses callouts, intermezzi and quotes}
\section{Introduction}
\toReview
Satisficing play was originally introduced
to try and limit the computation power that earlier models required of human
behavior \citep{herbert}. Originating from the field of economics, they
wanted to use a model that was not ``super intelligent''.

@@

\section{Core algorithm}
\toReview The core algorithm as presented by \citep{herbert} and formalized by
\citep{karandikar},
in here we present the simplified version of \citep{stimpson:2001} first:

@@

\section{Satisficing play in action}
\todo{make an intermezzo of this?}
\drafting
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma.
\fbox{
  \begin{minipage}{2.5in}
    \subsection{A prisoner's dillema introduction}
    The prisoner's dillema is one of the classical game thoery examples.
    Consider the following normal form game which is a prisoner's dillema:
    \begin{tabular}{lll}
                & Cooperate   & Defect \\
      Cooperate & $(2,2)$     & $(0,3)$  \\
      Defect    & $(3,0)$     & $(1,1)$  \\
    \end{tabular}
    The Nash equilibrium of this game lies on (Defect,Defect). However, all but
    that action are pareto optimal actions. So the Nash equilibrium would be the
    ``right'' strategy to play if the game is only played once, but if you repeat
    the game against the same opponent, interestingly enough you can ``solve''
    the prisoner's dilemma by ``teaching'' the opponent to cooperate.
    \todo{can one really solve? Is it really teaching? should either add references
    or change wording}
	\end{minipage}
	}
\drafting However strategies such as tit for tat or win stay lose shift already know
which actions are winning and which are punishing to try and solve it.
Satisficing play learns this however by updating the aspiration it got from
playing a move. If we consider a game versus always cooperate for example:

@@

\drafting In $t=0$ satisficing play doesn't meet its ambition of 4, therefore, in the
next game it modifies its ambition and changes its action. Here we can see
that satisficing play does get more utility than its ambition, and is satisfied
with its action.
But now if we start with a lower apsiration level:

@@

\drafting So here satisficing play finds a Pareto optimal action, but it doesn't find
the best possible action it could get against this opponent. From this example
we can also see how dependent satisficing play is on its starting parameters.
\todo{here we can interject an intermezzo, of how karandikar tried to solve
this with trajection and random perturbations}

@@

In this table we can see satisficing play and tit for tat ending up in a cycle.
at $t=0$ satisficing gained to little reward for its ambition level $\alpha_t$,
and therefore switches action in the next round. In $t=1$ saticificing play
is satisfied, but int $t=2$ it no longer is so it switches but this even ends
up being worse at $t=3$. After that the cycle resets at $t=4$, the cycle becomes
most obvious when looking at the $\pi_t$ column.
\section{Properties of satisficing play}
\drafting

Using both \citep{karandikar} and \citep{stimpson:2001} works to look deeper
at the properties of satisficing play.

@@

also showing the contrast graph which supports the work of \citep{arthur}

\section{An extended satisficing play}
\drafting

In here we discuss the work of \citep{stimpson:2003}, where he extends the
algorithm to be played with mutliple action choices.
Stimpson created a game where resources had to be allocated among agents.

\section{Satisficing compared to other learning methods}
\drafting

With help of the work of \citep{crandall} saticificing play is compared
to Q-learning and WOLF-PHC.
Q-learning is explained briefly with help of \citep{sandholm} and WOLF-PHC
with help of \citep{bowling}.

Finally some graphs are shown how they compare

@@

>>>>

\abstract{
  %TODO abstract
  \todo[inline]{abstract missing}
}
\todo{be more critical? maybe it depends to much on its paremeters?
  Or which game types are good for saticifing play?
}
\todo{misses callouts, intermezzi and quotes}
\section{Introduction}
\label{sec:introduction}
\toReview
Satisficing play was originally introduced
to try and limit the computation power that earlier models required of human
behavior \citep{herbert}. Originating from the field of economics, they
wanted to use a model that was not ``super intelligent''.

@@

\section{Core algorithm}
\label{sec:core-algorithm}
\toReview The core algorithm as presented by \citep{herbert} and formalized by
\citep{karandikar},
in here we present the simplified version of \citep{stimpson:2001} first:

@@

\section{Satisficing play in action}
\todo{make an intermezzo of this?}
\toReview
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma.
\fbox{
  \begin{minipage}{2.5in}
    \toReview
    \subsection{A prisoner's dillema introduction}
    The prisoner's dillema is one of the classical game theory examples.
    Consider the following normal form game which is a prisoner's dillema:
    \begin{tabular}{lll}
                & Cooperate   & Defect \\
      Cooperate & $(2,2)$     & $(0,3)$  \\
      Defect    & $(3,0)$     & $(1,1)$  \\
    \end{tabular}
    The Nash equilibrium of this game lies on (Defect,Defect). However, all but
    that action are pareto optimal actions. So the Nash equilibrium would be the
    ``right'' strategy to play if the game is only played once. However if you repeat
    the game against the same opponent you can ``solve''
    the prisoner's dilemma, meaning not playing the Nash equilibrium,
    but trying to get pareto optimal rewards. This
    is often done by starting defecting as soon as your opponent starts
    defecting, both the tit for tat and win stay lose shift strategies do this.
  \end{minipage}
}
\toReview Strategies such as tit for tat or win stay lose shift already know
which actions are winning and which are punishing to try and solve it.
Satisficing play learns this however by updating the aspiration it got from
playing a move. If we consider a game versus always cooperate for example:

@@

\toReview In $t=0$ satisficing play doesn't meet its ambition of 4, therefore, in the
next game it modifies its ambition and changes its action. Here we can see
that satisficing play does get more utility than its ambition, and is satisfied
with its action.
But now if we start with a lower apsiration level:

@@

\toReview So here satisficing play finds a Pareto optimal action, but it doesn't find
the best possible action it could get against this opponent. From this example
we can also see how dependent satisficing play is on its starting parameters.

\todo{here we can interject an intermezzo, of how karandikar tried to solve
this with trajection and random perturbations}

@@

In this table we can see satisficing play and tit for tat ending up in a cycle.
at $t=0$ satisficing gained to little reward for its ambition level $\alpha_t$,
and therefore switches action in the next round. In $t=1$ saticificing play
is satisfied, but int $t=2$ it no longer is so it switches but this even ends
up being worse at $t=3$. After that the cycle resets at $t=4$, the cycle becomes
most obvious when looking at the $\pi_t$ column. Also note about this opponent
that if saticificing play would've started with a lower aspiration, it would
not enter this cycle and just keep on cooperating.
\fbox{
  \begin{minipage}{2.5in}
    \toReview
    \subsection{Karandikar's algorithm}
    In the \nameref{sec:core-algorithm} section we said we would use Karandikar's
    notation, but use the simplified version of stimpson.
    Karandikar version would not necessarily change action when being
    disappointed (aspiration level not met), but would switch with a
    probability $p$, which he called \emph{inertia}.

    He also introduced another model, which used random perturbations on
    $\alpha_t$. This ``solved'', the initial state problem, however to prevent
    the random trembles to run out of hand relative to the game rewards the tremble
    generating function needed a feasible payoff interval $\Lambda$. Which
    requires more knowledge of the game, breaking the initial assumptions
    presented in the \nameref{sec:introduction}.
  \end{minipage}
}

\section{A saticificing comparison}
\drafting So, until now we've seen thoroughly how saticificing play works, and even some
strengths and weaknesses. However,

\todo{
With help of the work of \citep{crandall} saticificing play is compared
to Q-learning and WOLF-PHC.
Q-learning is explained briefly with help of \citep{sandholm} and WOLF-PHC
with help of \citep{bowling}.

Finally some graphs are shown how they compare
}

\section{Properties of satisficing play}
\drafting

\todo{
Using both \citep{karandikar} and \citep{stimpson:2001} works to look deeper
at the properties of satisficing play.

@@

also showing the contrast graph which supports the work of \citep{arthur}
}
\section{An extended satisficing play}
\drafting

\todo{
In here we discuss the work of \citep{stimpson:2003}, where he extends the
algorithm to be played with mutliple action choices.
Stimpson created a game where resources had to be allocated among agents.
}

@@

%  LocalWords:  Karandikar
